---
title: "Summary Report"
output:
  html_document: default
params:
  app_config: "app_config.csv"
  transaction_config: "transaction_config.csv"
---
<style type="text/css">
.main-container {
  max-width: 3000px;
  margin-left: 10px;
  margin-right: 10px;
}
hr.divider {
  border-top: 2px solid black;
}

details.description summary::after {
  content: attr(data-open);
  opacity: 0;
  font-size: 5px;
}

details.description[open] summary::after {
  content: attr(data-open);
  opacity: 1;
  font-size: 14px;
}
details.description summary::before {
  content: attr(data-close);
  opacity: 0;
  font-size: 5px;
}
details.description:not([open]) summary::before {
  content: attr(data-close);
  opacity: 1;
  font-size: 14px;
}
details.description summary::after,
details.description summary::before {
  display: inline-block;
  transition: all .4s ease-in-out;
  transform-origin: center bottom;
}

</style>

<br>
```{r set_color,results = 'asis', include=TRUE, echo = FALSE}
text_success="#008000"
text_failed="#e00000"
# background_success="#A5F5AB"
background_success="#EBFFE7"
# background_failure="#FFB7B7"FFE9E9
background_failure="#FFF2F2"

other_text_color="black"
```
```{r extract_timings,results = 'asis', include=TRUE, echo = FALSE}


start_time=format(as.POSIXct(as.double(test_results_markdown[1,c("start_time")]) / 1000, origin = "1970-01-01", tz = "EST"), "%Y-%m-%d %H:%M:%OS3")
end_time=format(as.POSIXct(as.double(test_results_markdown[1,c("end_time")]) / 1000, origin = "1970-01-01", tz = "EST"), "%Y-%m-%d %H:%M:%OS3")
```

```{r create_fileMapUpdated,results = 'asis', include=TRUE, echo = FALSE}
temp_result_filemap$merged=paste0("<b>",temp_result_filemap$temp_filename,"</b>: ",temp_result_filemap$filename)
files_namess=data.frame(subset(temp_result_filemap,testType=="base")$merged,subset(temp_result_filemap,testType=="current")$merged)
colnames(files_namess) <- c("base","current")
files_namess$base[duplicated(files_namess$base)] <- NA
files_namess$current[duplicated(files_namess$current)] <- NA
```


```{r overallSummary,results = 'asis', include=TRUE, echo = FALSE}

cat("<b>Note</b>: Results from this reports are generated using filtered data")

##Change file names to temporary names
for(i in 1:nrow(final_results)){
  
  if(!is.na(final_results[i,"baseFilename"])){
    base_fileName <- ""
    files <- strsplit(final_results[i,"baseFilename"], ",")[[1]]
    if(length(files)>1){
      for(f in files){
        if(base_fileName==""){
          base_fileName <- subset(temp_result_filemap,filename==trimws(f))$temp_filename
        }else{
          base_fileName <- paste0(base_fileName,", ",subset(temp_result_filemap,filename==trimws(f))$temp_filename)
        }
      }
    }else{
        if(!rlang::is_empty(files)){
          base_fileName=subset(temp_result_filemap,filename==trimws(files))$temp_filename
        }
    }

    final_results[i,"baseFilename"] <- base_fileName
  }
  
  if(!is.na(final_results[i,"currentFilename"])){
    current_fileName <- ""
    files <- strsplit(final_results[i,"currentFilename"], ",")[[1]]
    if(length(files)>1){
      for(f in files){
        if(current_fileName==""){
          current_fileName <- subset(temp_result_filemap,filename==trimws(f))$temp_filename
        }else{
          current_fileName <- paste0(current_fileName,", ",subset(temp_result_filemap,filename==trimws(f))$temp_filename)
        }
      }
    }else{
      if(!rlang::is_empty(files)){
        current_fileName=subset(temp_result_filemap,filename==trimws(files))$temp_filename
      }
    }

    final_results[i,"currentFilename"] <- current_fileName
  }
  
}

##Select result
if(weighted_comparision==TRUE & generate_vs_comparision_weighted){
  dat=subset(final_results,type=="standalone" | type=="weighted_comparison" | type=="comparison")
} else if(weighted_comparision==TRUE) {
  dat=subset(final_results,type=="standalone" | type=="weighted_comparison")
}else {
  if(base=="NA"){
    dat=subset(final_results,type=="standalone")   
  }else{
    dat=subset(final_results,type=="standalone" | type=="comparison")
  }
}



reactable(dat[,c("baseFilename","currentFilename","status","err_pct","type")],
    defaultColDef = colDef(
      # cell = function(value) format(value, nsmall = 1),
      align = "center",
      minWidth = 60,
      headerStyle = list(background = "#f7f7f8")
    ),
    columns = list(
      baseFilename=colDef(name="Base", align="center"),
      currentFilename=colDef(name="Current", align="center"),
      status=colDef(name="Status", align="center", maxWidth = 80,
         style = function(value) {
          if (value == "PASS") {
            color <- text_success
          } else if (value == "FAIL") {
            color <- text_failed
          }
          list(color = color, fontWeight = "bold")
         }
         ),
      err_pct=colDef(name="Total Transactions% with Error's", align="center", maxWidth = 120,
          cell = function(value) {
          paste0(value,"%")
          }),
      type=colDef(name="Type", align="center", maxWidth = 150)
    ),
  rowStyle = function(index) {
    if(final_results[index,"status"]=="PASS"){
      list(background = background_success, color = other_text_color )
    }else{
      list(background = background_failure, color = other_text_color )
    }
  },
  minRows = 1,
  outlined = TRUE, 
  defaultPageSize = 50,
  highlight = TRUE,
  resizable = TRUE,
  bordered = TRUE
  )



###Show table with tempFileName to actuall
reactable(files_namess,
  defaultColDef = colDef(
    align = "center",
    minWidth = 60,
    headerStyle = list(background = "#f7f7f8")
  ),
  columns = list(
    current=colDef(name="Current", align="center", minWidth = 200,
          html = TRUE),
    base=colDef(name="Base", align="center", minWidth = 200,
          html = TRUE)
  ),
  outlined = TRUE,
  highlight = TRUE,
  resizable = TRUE,
  bordered = TRUE
  )

  
rm(files_namess)
```

<hr>

```{r error_table_fun, results = 'asis', include=TRUE, echo = FALSE}
rect_error_table <- function(dat, title, totalTransactions, failedTransactions) {
  ret_err <- reactable(dat[,c("label","details")], 
  defaultColDef = colDef(
    align = "center",
    minWidth = 60,
    headerStyle = list(background = "#f7f7f8")
  ),
  columns = list(
    label=colDef(name="Transaction", minWidth=200, align="left"),
    details=colDef(name = "Error", minWidth=550, align="left",
          cell = function(value) {
          paste0("<ul>",value,"</ul")
          },
          html = TRUE)
  ),
    minRows = 1,
    outlined = TRUE, 
    pagination = FALSE,
    height = 400,
    filterable = TRUE,
    highlight = TRUE,
    # showPageSizeOptions = TRUE, 
    # pageSizeOptions = c(5, 10, 20, 30,40, 50,100,200),
    # defaultPageSize = 5,
    # paginationType = "jump",
    resizable = TRUE,
    bordered = TRUE,
    rowStyle = function(index) {
      list(color = other_text_color )
  })
  resultFile=title
  if(grepl('_VS_',title)){
    vsFiles <- strsplit(title,'_VS_')[[1]]
    title<- paste0(subset(temp_result_filemap,filename==vsFiles[1])$temp_filename,"_VS_",subset(temp_result_filemap,filename==vsFiles[2])$temp_filename)
  }else if(title!='Weighted_Comparision'){
    title <- subset(temp_result_filemap,filename==title)$temp_filename
  }
  
  cat("#### ",title,"   \n")
  cat(paste0("<p><b>",failedTransactions," transactions failed out of ",totalTransactions,"</b></p>"))
  cat(paste0("<p><b>Result</b>: ",resultFile,"</p>"))
  cat('\n')
  cat(as.character(htmltools::tagList(ret_err)))
  cat('\n')
}
```

### Errors {.tabset}
```{r summary_errors, results = 'asis', include=TRUE, echo = FALSE}

  # current_result_no
  if(weighted_comparision==TRUE){
      #Weighted Summary Error Tabs
      dat=subset(aggregated,check=="FAIL")
      title="Weighted_Comparision"
      totalTransactions=nrow(aggregated)
      failedTransactions=nrow(dat)
      rect_error_table(dat,title, totalTransactions,failedTransactions)
  }else {
    if(base=="NA") {
      #Current Test Error Tabs
      dat=subset(test_results_markdown,testType=="current" & no==1 & check=="FAIL")
      totalTransactions=nrow(subset(test_results_markdown,testType=="current" & no==1))
      failedTransactions=nrow(dat)
      title=dat[1,c("file")]
      rect_error_table(dat,title, totalTransactions,failedTransactions)
    }else{
      #Comparision Error Tabs
      comparisons <- unique(comparision_results_markdown[,c("vs")])
      for(i in comparisons) {
      	dat=subset(comparision_results_markdown,vs==i& check=="FAIL")
      	totalTransactions=nrow(subset(comparision_results_markdown,vs==i))
        failedTransactions=nrow(dat)
        title=i
        rect_error_table(dat,title, totalTransactions,failedTransactions)
      }
      #Current Test Error Tabs
      current_result <- subset(test_results_markdown,testType=="current")
      for(i in unique(current_result[,c("file")])) {
        dat=subset(test_results_markdown,file==i & check=="FAIL")
        totalTransactions=nrow(subset(test_results_markdown,file==i))
        failedTransactions=nrow(dat)
        title=dat[1,c("file")]
        rect_error_table(dat,title, totalTransactions,failedTransactions)
      }
    }
  }

```

<hr class="divider">

# Current Test {.tabset}

```{r currenTest, results = 'asis', include=TRUE, echo = FALSE}

base_name <- ""
for(file in strsplit(current, ",")[[1]]){
  title <- subset(temp_result_filemap,filename==get_filename(file))$temp_filename
  if(base_name==""){
    base_name <- title
    # base_name <- get_filename(file)
  }else{
    base_name <- paste0(base_name, ", ", title)
    # base_name <- paste0(base_name, ", ", get_filename(file))
  }
}

cat(paste0("<h5><b>",base_name,"</b></h5>"))
cat(paste0("<details class=\"description\" close><summary data-open=\"Close\" data-close=\"Show\"></summary></summary>"))
current_result <- subset(test_results_markdown,testType=="current")

for(i in unique(current_result[,c("file")])) {
  dat=filter(current_result,file==i)
  #Transactions
  ret <- reactable(dat[,c("label","check","avg","pc_95","sd","pass","fail","discard_pct","ci_95","kr","throughput","connect","receivedBytesPerSec","sentBytesPerSec","app")],
  defaultColDef = colDef(
    align = "center",
    minWidth = 60,
    headerStyle = list(background = "#f7f7f8"),
    footerStyle = list(fontWeight = "bold")
  ),
  columns = list(
    label=colDef(name="Transaction", minWidth=300, align="left",
      details = function(value) {
        if(dat[value,c("details")]!=""){
        paste0("<pre><ul>",dat[value,c("details")],"</ul></pre>")
        }
      },  html = TRUE,
    footer = "Total"),
    check=colDef(name = "Status", align="center",
         style = function(value) {
          if (value == "PASS") {
            color <- text_success
          } else if (value == "FAIL") {
            color <- text_failed
          }
          list(color = color, fontWeight = "bold")
         }, minWidth=100),
    avg = colDef(name="Average\nms", align="center", minWidth=100, footer = function(values) sprintf("%.2f", sum(values))),
    pc_95 = colDef(name = "95%\nms", align="center", minWidth=100, footer = function(values) sprintf("%.2f", sum(values))),
    sd = colDef(name="Std. Deviation", align="center", minWidth=100, footer = function(values) sprintf("%.2f", sum(values))),
    discard_pct = colDef(name="Discard%", format = colFormat(suffix = "%"), align="center", minWidth=100, footer = function(values) sprintf("%.2f", sum(values))),
    pass=colDef(name="Pass",align="center", minWidth=100, footer = function(values) sprintf("%.2f", sum(values))),
    fail=colDef(name="Fail",align="center", minWidth=100, footer = function(values) sprintf("%.2f", sum(values))),
    ci_95 = colDef(name = "Confidence\nInterval 95% ms", align="center", minWidth=100, footer = function(values) sprintf("%.2f", sum(values))),
    kr = colDef(name="Kurtosis", align="center", minWidth=100, footer = function(values) sprintf("%.2f", sum(values))),
    throughput = colDef(name="Throughput (TPS)", align="center", minWidth=100, footer = function(values) sprintf("%.2f", sum(values))),
    connect = colDef(name="Connect ms", align="center", minWidth=100, footer = function(values) sprintf("%.2f", sum(values))),
    receivedBytesPerSec = colDef(name="Received\n(KB/sec)", align="center", minWidth=100, footer = function(values) sprintf("%.2f", sum(values))),
    sentBytesPerSec = colDef(name="Sent\n(KB/sec)", align="center", minWidth=100, footer = function(values) sprintf("%.2f", sum(values))),
    app=colDef(name="App", align="center", minWidth=150)
  ),
  minRows = 1,
  pagination = FALSE,
  outlined = TRUE,
  height = 550,
  # searchable = TRUE,
  filterable = TRUE,
  onClick = "expand",
  highlight = TRUE,
  showSortIcon = TRUE,
  # showPageSizeOptions = TRUE,
  # pageSizeOptions = c(5, 10, 20, 30,40, 50,100,200),
  # defaultPageSize = 5,
  # paginationType = "jump",
  defaultExpanded = TRUE,
  resizable = TRUE,
  bordered = TRUE,
  rowStyle = function(index) {
    if(dat[index,"check"]=="PASS"){
      list(background = background_success, color = other_text_color )
    }else{
      list(background = background_failure, color = other_text_color )
    }
  }
  )
  
  start_time=format(as.POSIXct(as.double(dat[1,c("start_time")]) / 1000, origin = "1970-01-01", tz = "EST"), "%Y-%m-%d %H:%M:%OS3")
end_time=format(as.POSIXct(as.double(dat[1,c("end_time")]) / 1000, origin = "1970-01-01", tz = "EST"), "%Y-%m-%d %H:%M:%OS3")

  title <- subset(temp_result_filemap,filename==i)$temp_filename
  cat("## ",title,"   \n")
  cat(paste0("<p><b>",nrow(subset(dat, check=="FAIL"))," transactions failed out of ",nrow(dat),"</b></p>"))
  cat(paste0("<p><b>",nrow(subset(dat, check=="PASS" & details!=""))," warnings</b></p>"))
  cat(paste0("<p><b>Result</b>: ",i,"</p>"))
  cat(paste0("<p><b>","Time</b>: ",start_time,"  <b>-</b> ",end_time,"</p>"))
  
  cat('\n')
  cat(as.character(htmltools::tagList(ret)))
  cat('\n')

  cat(paste0("<details><summary><b>Warnings & Errors</b></summary>"))
  #Add details
  if(nrow(dat)>=1){
    for(i in 1:nrow(dat)){
      if(dat[i,c("details")]!=""){
        cat(paste0("<li>**",dat[i,c("label")],"**:<ul>",dat[i,c("details")]),"</ul></li>")
      }
    }
  }else{
    cat("No errors found<br />")
  }
  cat('</details>')
}

cat('</details>')

```
<!-- </details> -->

<hr>
<!-- <div class="container-fluid main-container"> -->
### Current test errors - JMeter {.tabset}
```{r current_errors, results = 'asis', include=TRUE, echo = FALSE}
cat(paste0("<h5><b>",base_name,"</b></h5>"))
cat(paste0("<details class=\"description\" close><summary data-open=\"Close\" data-close=\"Show\"></summary></summary>"))
for(i in unique(current_result[,c("file")])) {
  err=filter(test_errors_markdown,file==i)
  if(nrow(err)>0){
    ret_err <- reactable(err[,c("label","responseCode","failureMessage","fail")], 
  defaultColDef = colDef(
    align = "center",
    minWidth = 60,
    headerStyle = list(background = "#f7f7f8")
  ),
  columns = list(
    label=colDef(name="Transaction", minWidth=200, align="left"),
    responseCode=colDef(name = "Response Code", align="center"),
    failureMessage=colDef(name = "Error Message", minWidth=200, align="center"),
    fail=colDef(name = "Failures", align="center")
  ),
    minRows = 1,
    outlined = TRUE, 
    filterable = TRUE,
    pagination = FALSE,
    height = 550,
    highlight = TRUE,
    # showPageSizeOptions = TRUE, 
    # pageSizeOptions = c(5, 10, 20, 30,40, 50,100,200),
    # defaultPageSize = 5,
    # paginationType = "jump",
    resizable = TRUE,
    bordered = TRUE,
    rowStyle = function(index) {
      list(color = other_text_color )
  })
  
  resultFile=i
  title <- subset(temp_result_filemap,filename==i)$temp_filename
  
  cat("#### ",title,"   \n")
  cat('\n')
  cat(paste0("<p><b>Result</b>: ",resultFile,"</p>"))
  cat(as.character(htmltools::tagList(ret_err)))
  cat('\n')
  }else{
    cat("#### ",title,"   \n")
    cat('\n')
    cat(paste0("<p><b>Result</b>: ",resultFile,"</p>"))
    cat("No Errors found")
    cat('\n')    
  }
}
cat('</details>')
cat("<hr class=\"divider\">")
```
<!-- <hr class="divider"> -->
<!-- </div> -->

```{r , include=TRUE, echo = FALSE}
# rm(ret)
# rm(base_name)
# rm(dat)
```

<div class="container-fluid main-container">
```{r baseline, results = 'asis', include=TRUE, echo = FALSE}
if(base!="NA"){
  cat('# Baseline test {.tabset}   \n')
  base_name <- ""
  for(file in strsplit(base, ",")[[1]]){
    title <- subset(temp_result_filemap,filename==get_filename(file))$temp_filename
    if(base_name==""){
      base_name <- title
    }else{
      base_name <- paste0(base_name, ", ", title)
    }
  }
  
  cat(paste0("<h5><b>",base_name,"</b></h5>"))
  cat(paste0("<details class=\"description\" close><summary data-open=\"Close\" data-close=\"Show\"></summary></summary>"))
  base_result<- subset(test_results_markdown,testType=="base")
  
  for(i in unique(base_result[,c("file")])) {
    dat=filter(base_result,file==i)
    ret=reactable(dat[,c("label","check","avg","pc_95","sd","pass","fail","discard_pct","ci_95","kr","throughput","connect","receivedBytesPerSec","sentBytesPerSec","app")],
      defaultColDef = colDef(
        align = "center",
        minWidth = 60,
        headerStyle = list(background = "#f7f7f8"),
        footerStyle = list(fontWeight = "bold")
      ),
      columns = list(
        label=colDef(name="Transaction",minWidth=200, align="left",
          details = function(value) {
            if(dat[value,c("details")]!=""){
            paste0("<pre><ul>",dat[value,c("details")],"</ul></pre>")
            }
          }, html = TRUE, footer = "Total"),
        check=colDef(name="Status",align="center", minWidth=100,
         style = function(value) {
          if (value == "PASS") {
            color <- text_success
          } else if (value == "FAIL") {
            color <- text_failed
          }
          list(color = color, fontWeight = "bold")
         }),
        avg = colDef(name="Averag\nms",aggregate = "sum", align="center", minWidth=100, footer = function(values) sprintf("%.2f", sum(values))),
        pc_95 = colDef(name="95%\nms",aggregate = "sum", align="center", minWidth=100, footer = function(values) sprintf("%.2f", sum(values))),
        sd = colDef(name="Std. Deviation",aggregate = "sum", align="center", minWidth=100, footer = function(values) sprintf("%.2f", sum(values))),
        discard_pct = colDef(name="Discard%",aggregate = "sum",format = colFormat(suffix = "%"), align="center", minWidth=100, footer = function(values) sprintf("%.2f", sum(values))),
        pass=colDef(name="Pass",aggregate = "sum",align="center", minWidth=100, footer = function(values) sprintf("%d", sum(values))),
        fail=colDef(name="Fail",aggregate = "sum",align="center", minWidth=100, footer = function(values) sprintf("%d", sum(values))),
        ci_95 = colDef(name="Confidence Interval\n95% ms",aggregate = "sum", align="center", minWidth=100, footer = function(values) sprintf("%.2f", sum(values))),
        kr = colDef(name="Kurtosis",aggregate = "sum", align="center", minWidth=100, footer = function(values) sprintf("%.2f", sum(values))),
        throughput = colDef(name="Throughput (TPS)", align="center", minWidth=100, footer = function(values) sprintf("%.2f", sum(values))),
    connect = colDef(name="Connect ms", align="center", minWidth=100, footer = function(values) sprintf("%.2f", sum(values))),
    receivedBytesPerSec = colDef(name="Received\n(KB/sec)", align="center", minWidth=100, footer = function(values) sprintf("%.2f", sum(values))),
    sentBytesPerSec = colDef(name="Sent\n(KB/sec)", align="center", minWidth=100, footer = function(values) sprintf("%.2f", sum(values))),
        app=colDef(name="App",align="center", minWidth=150)
      ),
      minRows = 1,
      outlined = TRUE, 
      filterable = TRUE,
      highlight = TRUE,
      onClick = "expand",
      pagination = FALSE,
      height = 550,
      # showPageSizeOptions = TRUE, 
      # pageSizeOptions = c(5, 10, 20, 30,40, 50,100,200),
      # defaultPageSize = 5,
      # paginationType = "jump",
      defaultExpanded = TRUE,
      resizable = TRUE,
      bordered = TRUE,
      rowStyle = function(index) {
        if(dat[index,"check"]=="PASS"){
          list(background = background_success, color = other_text_color)
        }else{
          list(background = background_failure, color = other_text_color)
        }
      }
    )
    
   
  start_time=format(as.POSIXct(as.double(dat[1,c("start_time")]) / 1000, origin = "1970-01-01", tz = "EST"), "%Y-%m-%d %H:%M:%OS3")
end_time=format(as.POSIXct(as.double(dat[1,c("end_time")]) / 1000, origin = "1970-01-01", tz = "EST"), "%Y-%m-%d %H:%M:%OS3")
    

  resultFile=i
  title <- subset(temp_result_filemap,filename==i)$temp_filename
  
  cat("## ",title,"   \n")
  cat("")
  cat('\n')
  cat(paste0("<p><b>",nrow(subset(dat, check=="FAIL"))," transactions failed out of ",nrow(dat),"</b></p>"))
  cat(paste0("<p><b>",nrow(subset(dat, check=="PASS" & details!=""))," warnings</b></p>"))
  cat(paste0("<p><b>Result</b>: ",resultFile,"</p>"))
  cat(paste0("<p><b>","Time</b>: ",start_time,"  <b>-</b> ",end_time,"</p>"))
  cat(as.character(htmltools::tagList(ret)))
  cat('\n')
  
  cat(paste0("<details><summary><b>Warnings & Errors</b></summary>"))
  # cat("<b>Warnings & Errors:</b><br />")
  #Add details
  if(nrow(dat)>=1){
    for(i in 1:nrow(dat)){
      if(dat[i,c("details")]!=""){
        cat(paste0("<li>**",dat[i,c("label")],"**:<ul>",dat[i,c("details")]),"</ul></li>")
      }
    }
  }else{
    cat("No errors found<br />")
  }
  cat('</details>')
    
  
  }
  cat('</details>')
}

```
</div>



```{r , include=TRUE, echo = FALSE}
# rm(dat)
# rm(ret)
# rm(base_result)
```

<div class="container-fluid main-container">
```{r comprision, results = 'asis', include=TRUE, echo = FALSE}
  if((weighted_comparision!=TRUE  & base!="NA") | generate_vs_comparision_weighted){

  if(base!="NA"){
    cat("<hr class=\"divider\">")
    
     cat('# Comparison {.tabset}   \n')
     
     
     
     comparisons <- unique(comparision_results_markdown[,c("vs")])
     title <- ""
     for(i in comparisons) {
       vsFiles <- strsplit(i,'_VS_')[[1]]
       res<- paste0(subset(temp_result_filemap,filename==vsFiles[1])$temp_filename,"_VS_",subset(temp_result_filemap,filename==vsFiles[2])$temp_filename)
       if(title==""){
         title <- res
       }else{
         title <- paste0(title,", ",res)
       }
     }
  
        cat("<b>",title,"</b>")
     cat(paste0("<details class=\"description\" close><summary data-open=\"Close\" data-close=\"Show\"></summary></summary>"))
  
     for(i in comparisons) {
       dat=filter(comparision_results_markdown,vs==i)
       ret=reactable(dat[,c("label","check","pass.x","pass.y","fail.x","fail.y","avg.x","avg.y","avg_rpd","discard_pct.x","discard_pct.y","ci_95.x","ci_95.y","kr.x","kr.y","throughput.x","throughput.y","connect.x","connect.y","receivedBytesPerSec.x","receivedBytesPerSec.y","sentBytesPerSec.x","sentBytesPerSec.y","app")],
        defaultColDef = colDef(
          align = "center",
          minWidth = 60,
          headerStyle = list(background = "#f7f7f8"),
          footerStyle = list(fontWeight = "bold")
        ),
         columns = list(
           label=colDef(name="Transaction",minWidth=200, align="left",
            details = function(value) {
              if(dat[value,c("details")]!=""){
              paste0("<pre><ul>",dat[value,c("details")],"</ul></pre>")
              }
            }, html = TRUE, footer = "Total"),
           check=colDef(name="Status",align="center",
           style = function(value) {
            if (value == "PASS") {
              color <- text_success
            } else if (value == "FAIL") {
              color <- text_failed
            }
            list(color = color, fontWeight = "bold")
           }, minWidth=100),
           pass.x=colDef(name="Pass\nBaseline",align="center", minWidth=100, footer = function(values) sprintf("%d", sum(values))),
           pass.y=colDef(name="Pass Current",align="center", minWidth=100, footer = function(values) sprintf("%d", sum(values))),
           fail.x=colDef(name="Fail Baseline",align="center", minWidth=100, footer = function(values) sprintf("%.2f", sum(values))),
           fail.y=colDef(name="Fail Current",align="center", minWidth=100, footer = function(values) sprintf("%.2f", sum(values))),
           avg.x=colDef(name="Average Baseline ms",align="center", minWidth=100, footer = function(values) sprintf("%.2f", sum(values))),
           avg.y=colDef(name="Average Current ms",align="center", minWidth=100, footer = function(values) sprintf("%.2f", sum(values))),
           avg_rpd=colDef(name="Delta% Average",align="center",format = colFormat(suffix = "%"),
           cell = function(value) {
            paste0(value,"%")
            },
           style = function(value) {
            if (value > 0) {
              color <- text_success
            } else if (value < 0) {
              color <- text_failed
            } else {
              color <- "#777"
            }
            list(color = color, fontWeight = "bold")
           }, minWidth=100, footer = function(values) sprintf("%.2f", sum(values))),
           discard_pct.x=colDef(name="Discard% Baseline",align="center",format = colFormat(suffix = "%"),
           cell = function(value) {
            paste0(value,"%")
            }, minWidth=100, footer = function(values) sprintf("%.2f", sum(values))),
           discard_pct.y=colDef(name="Discard% Current",align="center",format = colFormat(suffix = "%"),
           cell = function(value) {
            paste0(value,"%")
            }, minWidth=100, footer = function(values) sprintf("%.2f", sum(values))),
           ci_95.x=colDef(name="Confidence Interval Baseline ms",align="center", minWidth=100, footer = function(values) sprintf("%.2f", sum(values))),
           ci_95.y=colDef(name="Confidence Interval Current ms",align="center", minWidth=100, footer = function(values) sprintf("%.2f", sum(values))),
           kr.x = colDef(name="Kurtosis Baseline",aggregate = "sum", align="center", minWidth=100, footer = function(values) sprintf("%.2f", sum(values))),
           kr.y = colDef(name="Kurtosis Current",aggregate = "sum", align="center", minWidth=100, footer = function(values) sprintf("%.2f", sum(values))),
           throughput.x = colDef(name="Throughput Baseline (TPS)", align="center", minWidth=100, footer = function(values) sprintf("%.2f", sum(values))),
           throughput.y = colDef(name="Throughput Current (TPS)", align="center", minWidth=100, footer = function(values) sprintf("%.2f", sum(values))),
           connect.x = colDef(name="Connect Baseline ms", align="center", minWidth=100, footer = function(values) sprintf("%.2f", sum(values))),
           connect.y = colDef(name="Connect Current ms", align="center", minWidth=100, footer = function(values) sprintf("%.2f", sum(values))),
           receivedBytesPerSec.x = colDef(name="Received\n(KB/sec) Baseline", align="center", minWidth=100, footer = function(values) sprintf("%.2f", sum(values))),
           receivedBytesPerSec.y = colDef(name="Received\n(KB/sec) Current", align="center", minWidth=100, footer = function(values) sprintf("%.2f", sum(values))),
           sentBytesPerSec.x = colDef(name="Sent\n(KB/sec Baseline)", align="center", minWidth=100, footer = function(values) sprintf("%.2f", sum(values))),
           sentBytesPerSec.y = colDef(name="Sent\n(KB/sec) Current", align="center", minWidth=100, footer = function(values) sprintf("%.2f", sum(values))),
           app=colDef(name="App",align="center", minWidth=150)
         ),
        minRows = 1,
        outlined = TRUE,
        filterable = TRUE,
        pagination = FALSE,
        height = 550,
        onClick = "expand",
        highlight = TRUE,
        # showPageSizeOptions = TRUE,
        # pageSizeOptions = c(5, 10, 20, 30,40, 50,100,200),
        # defaultPageSize = 5,
        # paginationType = "jump",
        bordered = TRUE,
        resizable = TRUE,
        defaultExpanded = TRUE,
        rowStyle = function(index) {
          if(dat[index,"check"]=="PASS"){
            list(background = background_success, color = other_text_color)
          }else{
            list(background = background_failure, color = other_text_color)
          }
        }
    )
       
       
    if(grepl('_VS_',i)){
      vsFiles <- strsplit(i,'_VS_')[[1]]
      title<- paste0(subset(temp_result_filemap,filename==vsFiles[1])$temp_filename,"_VS_",subset(temp_result_filemap,filename==vsFiles[2])$temp_filename)
    }
    
      cat("## ",title,"   \n")
      cat("")
      cat('\n')
      cat(paste0("<p><b>",nrow(subset(dat, check=="FAIL"))," transactions failed out of ",nrow(dat),"</b></p>"))
      cat(paste0("<p><b>",nrow(subset(dat, check=="PASS" & details!=""))," warnings</b></p>"))
      cat(paste0("<p><b>Result</b>: ",i,"</p>"))
      cat(as.character(htmltools::tagList(ret)))
      cat('\n')
      
      cat(paste0("<details><summary><b>Warnings & Errors</b></summary>"))
    
    
    # Add details
    if(nrow(dat)>=1){
        for(i in 1:nrow(dat)){
          if(dat[i,c("details")]!=""){
            cat(paste0("<li>**",dat[i,c("label")],"**:<ul>",dat[i,c("details")]),"</ul></li>")
          }
        }
      }else{
        cat("No errors found<br />")
      }
    cat('</details>')
    
    }
    cat('</details>')
  }
}
```

```{r comprision_weighted, results = 'asis', include=TRUE, echo = FALSE}

if(weighted_comparision == TRUE){
  
   cat("<hr>")
  
    base_name=""
    temp_rest_name_base=""
    for(file in unique(subset(test_results_markdown,testType=="base")$file)){
      base_temp=subset(temp_result_filemap,filename==get_filename(file))$temp_filename
      if(base_name==""){
        base_name <- get_filename(file)
        temp_rest_name_base <- base_temp
      }else{
        base_name <- paste0(base_name, ", ", get_filename(file))
        temp_rest_name_base <- paste0(temp_rest_name_base, ", ", base_temp)
      }
    }
    current_name=""
    temp_rest_name_current=""
    for(file in unique(subset(test_results_markdown,testType=="current")$file)){
      current_temp=subset(temp_result_filemap,filename==get_filename(file))$temp_filename
      if(current_name==""){
        current_name <- get_filename(file)
        temp_rest_name_current <- current_temp
      }else{
        current_name <- paste0(current_name, ", ", get_filename(file))
        temp_rest_name_current <- paste0(temp_rest_name_current, ", ", current_temp)
      }
    }
  
  ret_weighted <- reactable(aggregated[c("label","check","pass.x","pass.y","fail.x","fail.y","avg.x","avg.y","delta","ci_95.x","ci_95.y","sd.x","sd.y","kr.x","kr.y","discard_pct.x","discard_pct.y","throughput.x","throughput.y","connect.x","connect.y","receivedBytesPerSec.x","receivedBytesPerSec.y","sentBytesPerSec.x","sentBytesPerSec.y")],
    defaultColDef = colDef(
      align = "center",
      minWidth = 60,
      headerStyle = list(background = "#f7f7f8"),
      footerStyle = list(fontWeight = "bold")
    ),
    columns = list(
            label=colDef(name="Transaction", minWidth=300,maxWidth=300, align="left", style = list(position = "sticky", left = 0, background = "#fff", zIndex = 1),headerStyle = list(position = "sticky", left = 0, background = "#f7f7f8", zIndex = 1),
        details = function(value) {
        
        if(aggregated[value,c("details")]!=""){
          as.character(paste0("<pre><ul>",aggregated[value,c("details")],"</ul></pre>"))
        }
      }, html = TRUE, footer = "Total"),
      check=colDef(name="Status",align="center", minWidth=100,
          style = function(value) {
          if (value == "PASS") {
            color = text_success
            background = background_success
          } else if (value == "FAIL") {
            color = text_failed
            background = background_failure
          }
          list(color = color, fontWeight = "bold", position = "sticky", left = 300, background = background, zIndex = 1)
         },headerStyle = list(position = "sticky", left = 300, background = "#f7f7f8", zIndex = 1)),
      pass.x=colDef(name="Pass Baseline",align="center", minWidth=100, footer = function(values) sprintf("%d", sum(values))),
      pass.y=colDef(name="Pass Current",align="center", minWidth=100, footer = function(values) sprintf("%d", sum(values))),
      fail.x=colDef(name="Fail Baseline",align="center", minWidth=100, footer = function(values) sprintf("%d", sum(values))),
      fail.y=colDef(name="Fail Current",align="center", minWidth=100, footer = function(values) sprintf("%d", sum(values))),
      avg.x=colDef(name="Average Baseline ms",align="center", minWidth=100, footer = function(values) sprintf("%.2f", sum(values))),
      avg.y=colDef(name="Average Current ms",align="center", minWidth=100, footer = function(values) sprintf("%.2f", sum(values))),
      delta=colDef(name="Delta%",align="center", minWidth=100,
         cell = function(value) {
          paste0(value,"%")
          },
         style = function(value) {
          if (value > 0) {
            color <- text_success
          } else if (value < 0) {
            color <- text_failed
          } else {
            color <- "#777"
          }
          list(color = color, fontWeight = "bold")
         }, footer = function(values) sprintf("%.2f", sum(values))),
      ci_95.x=colDef(name="Confidence Interval Baseline 95% ms",align="center", minWidth=100, footer = function(values) sprintf("%.2f", sum(values))),
      ci_95.y=colDef(name="Confidence Interval Current 95% ms",align="center", minWidth=100, footer = function(values) sprintf("%.2f", sum(values))),
      sd.x=colDef(name="Std. Deviation Baseline",align="center", minWidth=100, footer = function(values) sprintf("%.2f", sum(values))),
      sd.y=colDef(name="Std. Deviation Current",align="center", minWidth=100, footer = function(values) sprintf("%.2f", sum(values))),
      kr.x=colDef(name="Kurtosis Baseline",align="center", minWidth=100, footer = function(values) sprintf("%.2f", sum(values))),
      kr.y=colDef(name="Kurtosis Current",align="center", minWidth=100, footer = function(values) sprintf("%.2f", sum(values))),
      discard_pct.x=colDef(name="Discard% Baseline",align="center", minWidth=100, footer = function(values) sprintf("%.2f", sum(values))),
      discard_pct.y=colDef(name="Discard% Current",align="center", minWidth=100, footer = function(values) sprintf("%.2f", sum(values))),
      throughput.x = colDef(name="Throughput Baseline (TPS)",aggregate = "sum", align="center", minWidth=100, footer = function(values) sprintf("%.2f", sum(values)),format = colFormat(digits = 2)),
      throughput.y = colDef(name="Throughput Current (TPS)",aggregate = "sum", align="center", minWidth=100, footer = function(values) sprintf("%.2f", sum(values)),format = colFormat(digits = 2)),
      connect.x = colDef(name="Connect Baseline ms",aggregate = "sum", align="center", minWidth=100, footer = function(values) sprintf("%.2f", sum(values)),format = colFormat(digits = 2)),
      connect.y = colDef(name="Connect Current ms",aggregate = "sum", align="center", minWidth=100, footer = function(values) sprintf("%.2f", sum(values)),format = colFormat(digits = 2)),
      receivedBytesPerSec.x = colDef(name="Received\n(KB/sec) Baseline",aggregate = "sum", align="center", minWidth=100, footer = function(values) sprintf("%.2f", sum(values)),format = colFormat(digits = 2)),
      receivedBytesPerSec.y = colDef(name="Received\n(KB/sec) Current",aggregate = "sum", align="center", minWidth=100, footer = function(values) sprintf("%.2f", sum(values)),format = colFormat(digits = 2)),
      sentBytesPerSec.x = colDef(name="Sent\n(KB/sec) Baseline",aggregate = "sum", align="center", minWidth=100, footer = function(values) sprintf("%.2f", sum(values)),format = colFormat(digits = 2)),
      sentBytesPerSec.y = colDef(name="Sent\n(KB/sec) Current",aggregate = "sum", align="center", minWidth=100, footer = function(values) sprintf("%.2f", sum(values)),format = colFormat(digits = 2)),
      app=colDef(name="App",align="center", minWidth=150)
    ),
      minRows = 1,
      outlined = TRUE, 
      filterable = TRUE,
      highlight = TRUE,
      pagination = FALSE,
      height = 600,
      onClick = "expand",
      # showPageSizeOptions = TRUE, 
      # pageSizeOptions = c(5, 10, 20, 30,40, 50,100,200),
      # defaultPageSize = 5,
      # paginationType = "jump",
      resizable = TRUE,
      wrap = TRUE,
      bordered = TRUE,
      defaultExpanded = TRUE,
      rowStyle = function(index) {
        if(aggregated[index,"check"]=="PASS"){
          list(background = background_success, color = other_text_color)
        }else{
          list(background = background_failure, color = other_text_color)
        }
      }
    )
  
  cat("### Comparison - weighted  \n")
  cat(paste0(" <b>Average of Baseline Tests</b>: ",temp_rest_name_base,"<br>",
             "&emsp;&emsp;&emsp;&emsp;&emsp;&emsp;&emsp;&emsp;&emsp;&emsp;&emsp;&emsp;<b>VS</b><br>",
             " <b>Average of Current Tests</b>:",temp_rest_name_current,"<br>"))
  # Comparison Same Table no Sub Tabs
  cat(paste0("<details class=\"description\" close><summary data-open=\"Close\" data-close=\"Show\"></summary>"))
  cat(paste0("<p><b>",nrow(subset(aggregated, check=="FAIL"))," transactions failed out of ",nrow(aggregated),"</b></p>"))
  cat(paste0("<p><b>",nrow(subset(dat, check=="PASS" & details!=""))," warnings</b></p>"))
  cat(paste0("<p><b>Average of Baseline Tests</b>: ",base_name,"</p>"))
  cat(paste0("<p><b>Average of Current Tests</b>: ",current_name,"</p>"))
  cat("\n")
  cat(as.character(htmltools::tagList(ret_weighted)))
  cat(paste0("<details><summary><b>Warnings & Errors</b></summary>"))
  
  # Add details
  if(nrow(aggregated)>=1){
      for(i in 1:nrow(aggregated)){
        if(aggregated[i,c("details")]!=""){
          cat(paste0("<li>**",aggregated[i,c("label")],"**:<ul>",aggregated[i,c("details")]),"</ul></li>")
        }
      }
    }else{
      cat("No errors found<br />")
    }
  cat('</details>')
  cat('</details>')
cat("<hr class=\"divider\">")
}
```
</div>
<br>